---
title: "Womens Rights and Terrorism Analysis"
author: "Sophia Deng, Kat Fan, Jiayu Li, Siyuan Lu, and Angela Zhao"
date: "2023-12-19"
output:
   pdf_document: default
---

```{r setup, include=FALSE}
# Packages to include that are needed for setup
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(haven)
# Library Countrycode is used to convert the country code to a country 
library(countrycode)
library(MASS)
```


Loading data:
```{r}
rep_dataset <- read_dta("jfh_replicationdataset.dta")
```

## Analysis 1
### Poisson v. Binomial Regression

```{r}
# poisson
poisson_model <- glm(terrordomestic ~ physint + womenscale + xconst + lngdp + lnpop + coldwar, data = rep_dataset, family = poisson())

summary(poisson_model)

# negbin
negbin_model <- glm.nb(terrordomestic ~ physint + womenscale + xconst + lngdp + lnpop + coldwar, data = rep_dataset)

summary(negbin_model)


```


## Analysis 2
### Regressing terrordomestic for high women's rights countries 
```{r}
# terrordomestic regressed on physint womenscale xconst lngdp lnpop coldwar, fe
rep_women_9<- rep_dataset[rep_dataset$womenscale>=7,]
new_lm <- lm(terrordomestic ~ physint + womenscale + xconst + lngdp + lnpop + coldwar,data = rep_women_9)
print(summary(new_lm))

```

## Analysis 3
### Regressing terrordomestic for low women's rights countries 
```{r}
rep_women_9<- rep_dataset[rep_dataset$womenscale<=3,]
new_lm <- lm(terrordomestic ~ physint + womenscale + xconst + lngdp + lnpop + coldwar,data = rep_women_9)
print(summary(new_lm))

```


## Analysis 4
### Regressing transnational terrorism for low women's rights countries 
```{r}
rep_women_9<- rep_dataset[rep_dataset$womenscale<=3,]
new_lm <- lm(transevents ~ physint + womenscale + xconst + lngdp + lnpop + coldwar,data = rep_women_9)
print(summary(new_lm))

```

## Analysis 5
### Regressing transnational terrorism for high women's rights countries
```{r}
rep_women_9<- rep_dataset[rep_dataset$womenscale>=7,]
new_lm <- lm(transevents ~ physint + womenscale + xconst + lngdp + lnpop + coldwar,data = rep_women_9)
print(summary(new_lm))

```


## Analysis 6
### Graph of regression of womens rights against domestic terrorism based on countries with high correlation
```{r}
df <- data.frame()
all_countries <- unique(rep_dataset$ccode)
n <- length(all_countries)
w_i <- rep(NA,n )
w_s <- rep(NA,n)

# translating COW code to country name 
df <- data.frame(women_terrorism_intercept = w_i,women_terrorism_slope = w_s, COWcode = all_countries)
df$countryname <- countrycode(df$COWcode, "cown", "country.name")

for (i in 1:n){
  curr_country <- all_countries[i]
  domestic_i <- rep_dataset$terrordomestic[rep_dataset$ccode==curr_country]
  womenscale_i <- rep_dataset$womenscale[rep_dataset$ccode==curr_country]
  lm_res <- lm(domestic_i ~ womenscale_i)
  df$women_terrorism_intercept[i] <- coef(lm_res)["(Intercept)"]
  df$women_terrorism_slope[i] <-coef(lm_res)["womenscale_i"]
}
df <- na.omit(df)
# Getting the top ten highest positively correlated countries
df_top_10 <- df[order(df$women_terrorism_slope,decreasing=TRUE),]
df_top_10 <- df_top_10[1:10,]
p <- ggplot(data = df_top_10)
p <- p + geom_col(aes(x = reorder(countryname,women_terrorism_slope), y = women_terrorism_slope,fill = countryname))
p <- p + theme_bw()
p <- p + theme(axis.text.x=element_text(angle=60,hjust=1)) 
p <- p + xlab("Country")
p <- p + ylab("Women's Rights v. Terrorism Slope")
show(p)

```

### Graph of regression of womens rights against domestic terrorism based on countries with low correlation
```{r}

df <- na.omit(df)
df_bottom_10 <- df[order(df$women_terrorism_slope,decreasing=FALSE),]

# Getting the top ten lowest correlated countries
df_bottom_10 <- df_bottom_10[1:10,]
p <- ggplot(data = df_bottom_10)
p <- p + geom_col(aes(x = reorder(countryname,women_terrorism_slope), y = women_terrorism_slope,fill = countryname))
p <- p + theme_bw()
p <- p + theme(axis.text.x=element_text(angle=60,hjust=1)) 
p <- p + xlab("Country")
p <- p + ylab("Women's Right v. Terrorism Slope")

show(p)

```


## Determining how many unique Countries there are:
```{r}
cat('There are', length(unique(rep_dataset$ccode)),'unique Country IDs \n')
ccode_factor <- table(rep_dataset$ccode)
count_df <- as.data.frame(ccode_factor)
kable(list(count_df[1:30,],count_df[31:60,],count_df[61:90,],count_df[91:120,],count_df[121:150,]), col.names = c("CCode","Count"),row.names = FALSE )%>%
  kable_styling(latex_options = "HOLD_position")
```


